factor_explorer

### 2014-06-22 ijlyttle/factor_explorer.Rmd
converts some student2012 variables, like starting age, to factor

>>>>

```{r make_factors}
fn_make_factor <- function(vec){  
  vec <- factor(vec, levels = sort(unique(vec)))
}

# hacky - fix when time
student2012$ST01Q01 <- fn_make_factor(student2012$ST01Q01)
student2012$ST02Q01 <- fn_make_factor(student2012$ST02Q01)
student2012$ST06Q01 <- fn_make_factor(student2012$ST06Q01)
student2012$ST21Q01 <- fn_make_factor(student2012$ST21Q01)
student2012$ST115Q01 <- fn_make_factor(student2012$ST115Q01)

```
